Playfair and the \"Flatten the Curve\" Graphic

### 2022-02-19 _posts/2022-02-19-playfair-and-the-flatten-the-curve-graphic/playfair-and-the-flatten-the-curve-graphic.Rmd
update thumb size limit, build

---
title: "Playfair and the \"Flatten the Curve\" Graphic"
description: |
  The importance of simplicity in statistical graphics
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-02-19
output:
  distill::distill_article:
    self_contained: false
categories:
  - tufte
  - design
bibliography: bib.bib
preview: nyt_curve.png
---

>>>>

---
title: "Playfair and the \"Flatten the Curve\" Graphic"
description: |
  The importance of simplicity in statistical graphics
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-02-19
output:
  distill::distill_article:
    self_contained: false
bibliography: bib.bib
preview: nyt_curve.png
categories:
  - tufte
  - design
---
